\chapter{Introduction}
Communication technology can today be seen as a foundation for a wide range of technologies. Devices today can communicate with each other in many different ways, and can take part in large and small networks alike.

This report resolves around embedded systems and how communication can be established between these. This focus point is quite broad in terms of application usages, so this report will deal with a specific use case to demonstrate the communication between embedded systems and its applied usage.

The use case that will be in focus throughout the report is the ground information of a golf course, where multiple devices will report information about the soil, to a central unit.

%If a device is placed out of range from the central unit, it will need to send the its data reading to the central unit by using other devices within reach.

To ensure that the data will reach the central unit and that it is still intact, an adequate communication protocol and module should be implemented. The protocol and module must be applicable on the embedded devices, to allow for the data communication. 

\section*{Initializing problem statement}
To initialize and give foundation for an analysis, a temporary problem statement is formulated:

\textit{Can embedded systems be utilized to assist in maintaining a golf course?}

%\section{OLD Initializing problem statement}\todo{remove this, redundant, final problem statement might be similar to this.}

%\textit{How can a sensor network and a protocol be designed, so that data can be relayed throughout the network, enabling an endpoint device to receive the information without being within range of all sensors in the network?}
