\chapter{Reading instructions}
\todo{subsection under introduction instead?}
This chapter contains definitions for some of the terms throughout the report. The report is intended to be read in sequential order, to fully comprehend the content and development.

\section*{Definition list}
The definition of some terms is described here, to ensure unambiguity.\todo{longer metatext/motivation}

\begin{description}
\item[Mesh network] \hfill \\
A network with multiple nodes, using each other to transfer data. Meaning that if Node 1 and Node 5 is not in range of each other, they will use nodes inbetween them, for example Nodes 2, 3, and 4, to transport the data.\todo{mesh metwork not as relevant, as the topology is tree}

\item[Node / sensor node] \hfill \\
The nodes in the network used to read sensor data and relay information from other sensor nodes.

\item[Main node] \hfill \\
The node that starts requests and collects data from sensor nodes. The main node has a user interface to start requests and display data to users.

\item[Radio module] \hfill \\
This refers to the wireless communication component used in the solution, which is tasked with sending and receiving data from and to other nodes.

\item[Request] \hfill \\
A term used for when the main node sends a request packet, a sensor reading demand by the user. Makes sensor nodes read and send or relay data back to the main node.

\item[Packet] \hfill \\
A message, consisting of data and metadata, transmitted using radio modules between two nodes.

\end{description}
