\section{RF24 testing}
The following section contains the tests performed on the RF24 radio module. These tests were performed to determine how 

\subsection{RF24 reliability}
The first test performed on the RF24 is a reliability test. This test is performed using one sender and one receiver device. The objective of the test is to determine the number of packets lost from one device to another. 
The code used in this test can be found in Appendix \ref{cha:reliabilityCode}.


The sender device sends a number of packets before stopping, e.g. 10000 or more, using a delay between each package, though the delay can be removed. For every packet sent, the sender increments a counter value.

The receiver accepts packets, and for every packet received it increments a counter value. This value is printed to the console, to allow the tester to track the number of packets received.

Multiple delay values were tested, including no delay used. During these tests, only one packet did not reach the receiver, when using no delay at all. This could be due to a number of things, but most likely the receiver did not print the value to the console due to speed or the sender started before the receiver.

The conclusion to the reliability test is that the RF24 is more than reliable enough for the requirements of this project.


%\subsection{RF24 transreciever analysis}
%To confirm the usability of the RF24 transreciever, labeled as RF24 from this point, a short analysis with tests will be performed.

\subsection{Range}
A basic test to test the range is useful to ensure that RF24 is usable in a practical application with a wide distance between units.

%\subsection{Testing method:}
Testing is done by having two units set as transmitter and reciever units respectively, having the transmitter transmit a single signal repeatedly while increasing the distance between the units. When the reciever no longer recieves the signal, the distance can then be measured.

CODE GOES HERE! \todo{set some code in here}

%\subsection{Results:}
\begin{table}[!h]
\begin{tabular}{|l|l|l|l|} \hline
	\diaghead{\theadfont Diag ColumnmnHead II} {Reciever}{Transmitter}
			& Unit 1 	& Unit 2 	& Unit 3 	\\\hline
	Unit 1  	& - 		& ? 		& ? 		\\\hline
	Unit 2  	& ? 		& - 		& ? 		\\\hline
	Unit 3  	& ? 		& ? 		& - 		\\\hline
\end{tabular}
\end{table}

\iffalse %Kommmentarblok
\subsection{Bit error rate:}
what is?

%\subsection{Testing method}:
how? code, setup etc.

%\subsection{Results:}
\begin{table}[!h]
\begin{tabular}{|l|l|l|l|} \hline
	Datasheet 	& Unit 1 	& Unit 2 	& Unit 3 	\\\hline
	0,0\% 		& ? 		& ? 		& ? 		\\\hline
\end{tabular}
\end{table}
\fi %Afslutted kommentarblok

\subsection{Bit Error Rate}
When transmitting data from one unit to another, knowing that the data is correct can be important. To get an idea of how much error is introduced in the communication, a bit error test can be performed, known as BERT from this point.

\textbf{About BERT}

The basic concept of BERT is to send a known datastream from one unit to another, and check how much it differs from the expected datastream. As the RF24 is a radio transceiver there's possible factors as range and noise. \todo{source}

The duration of a BERT should vary depending on the results. To get an exact result it would have to take an infinite amount of time, which of course is not feasible. But du to the nature of randomness, if only a small amount of errors are met, then it could just be a "lucky"\todo{formulate}  test, so the testing length would have to be sufficiently long for getting a general idea.

\textbf{Executing BERT} 

Noise generated by another transceiver near the recieving point.

The code running on the arduinos for the test is:

Sender:
Code sending some deterministic value

Reciever:
Code accepting some value, and checks verifyes it against same method it was generated by.
Keeps track of amount of correct and wrong values

The BER test was executed four times. The first three times with one million packets transmitted, and the fourth time with ten million packets. For every one thousand packet received, the number of errors and successes were printed for that thousand packet. 

The complete spreadsheet with results and graphs can be found on the attached DVD. 

\textbf{Result of BERT}

%primarysource http://www.radio-electronics.com/info/rf-technology-design/ber/bit-error-rate-testing-bert.php
