\label{cha:technologies}
There are multiple technologies available to utilize in a solution. This chapter contains information, descriptions and examinations of the considered technologies, as well as definitions used later in the report.

First, the power source for the nodes are examined, and then controller units for the sensors will be described. Secondly, sensor devices are studied to be able to choose an adequate unit for the solution. Thirdly, communication devices are examined to select an appropriate unit to use in the solution. 

In the last part of the chapter, network topologies and communication protocols are examined to explore ways to implement a network of nodes transmitting sensor data. The chosen components, network type, and protocol can be found in chapter \ref{cha:designintro}.

\input{chapters/analysis/technologies/arduino.tex}

\input{chapters/analysis/technologies/powerSupply.tex}

\input{chapters/analysis/technologies/sensors.tex}

\input{chapters/analysis/technologies/communicationDevices.tex}

\input{chapters/analysis/technologies/networks.tex}

\input{chapters/analysis/technologies/protocols.tex}

\chapter{Data transmission}
In this chapter the theory and considerations on data transmission are described. First, exponential backoff is described, which helps reduce interference and collisions. Next are techniques to verify that data transmitted are not received as corrupted, obfuscated or in any other way different from the actual data transmitted.

\input{chapters/analysis/technologies/interference.tex}

\input{chapters/analysis/technologies/crc.tex}
